Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-26 Docs/IJES/journal.tex
review 4.3 Multi-core ESBMC with OpenMP (ESBMC-SS)

Typically, ESBMC verification runs are performed only in a single-core. If the processor provides $8$ processing cores, only one is used for the verification and the others remain idle. Thus, there is a significant unused hardware resource during this process.

@@

ESBMC-SS obtains the problem specification represented by a ANSI-C program. The HW-SW partitioning is violated, when the correct optimum value (\textit{TipH}) parameter is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores. All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}. Note that there is no shared-memory (or message-passing) mechanism among threads. In particular, different threads are managed by the OpenMP API, which is responsible for the thread life-cycle: start, running, and dead states, using different values as condition. After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment. During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time. If all threads of the batch processing are terminated, then ESBMC-SS finishes its execution.

>>>>

Typically, ESBMC verification runs are performed only in a single-core. If the processor provides $n$ processing cores, only one is used for the verification and the others remain idle. Thus, there is a significant unused hardware resource during this process.

@@

ESBMC-SS obtains the problem specification represented by an ANSI-C program. The HW-SW partitioning is violated, when the correct optimum value parameter (represented by $TipH \in \mathbb{N}$) is reached; ESBMC-SS starts a parallel region with different instances of ESBMC, based on the number of available processing cores. All these ESBMC instances run independently of each other, as shown in Fig.~\ref{ESBMC-Multi-core}. Note that there is no shared-memory (or message-passing) mechanism among threads. In particular, different threads are managed by the OpenMP API, which is responsible for managing the thread life-cycle: start, running, and dead states, using different values as condition. After executing $N$ instances, if there is no code violation, then ESBMC-SS starts new instances again; this represents a sequential-search on a multi-core environment. During the parallel region execution, if a violation is found in any running thread, then it presents a counterexample with the violation condition and the verification time. If all threads of the batch processing are terminated, then ESBMC-SS finishes its execution.
